Cryptographic assurance of secrecy and fairness in voting

### 2012-12-05 paper/paper.tex
Add coercion resistance

It is often necessary to maintain secrecy of invididuals' votes, to avoid the possibility
that a voter may receive either retribution or reward.
We give two definitions of ballot secrecy: \term{privacy} and \term{receipt-freeness}.

@@

>>>>

The intent of an election is to determine the true will of the voters.
If there is any possibility for a third party to discover the content of
an individual's ballot, then the voter's own will may be undermined by coercion.
Therefore a voting system must maintain secrecy of invididuals' votes to avoid
the possibility that a voter may receive retribution or reward for casting a vote
in any particular way.

We give multiple definitions of ballot secrecy in order of increasing strength:
\term{privacy}, \term{receipt-freeness}, and \term{coercion resistance}.

@@

\subsection{Coercion resistance}
